---
title: "Car Predictor Webapp"
author: "Will G"
date: "December 17, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background 

- Its hard to decide what is more important: Fuel Economy or Performance?
- The Car Predictor makes the decision for you!
- Application link: https://wg68data.shinyapps.io/will_g_car_predictor/
- Github link https://github.com/wtg5020/devdataproductsfinal
- Allows user to select transmission type, number of cylinders, horsepower, and car weight
- Outputs estimated MPG and Quarter Mile time as well as a list of existing cars that satisfy the calculations

## Prediction Model Example

The prediction model for the application is below, here the inputs have been simulated for a car weighing 1000 lbs with a 4 cylinder engine thats 90hp with an automatic transmission. The output of the model is also printed as 28.313 MPG

```{r, echo = TRUE}
modelMul <- lm(mpg ~ wt + cyl + hp + am, data=mtcars)
mpgP <- predict(modelMul, newdata = 
    data.frame(wt = 1, cyl = 4, hp = 90, am = 0))
print(mpgP)
```

## Data Table Example
Data Table output based on prediction
```{r, echo = TRUE}
dataTable <- cbind(names = rownames(mtcars), mtcars)
dataTableSelect <- dataTable[, c("names", "mpg", 
                              "cyl", "hp", "wt", "qsec")] 
modelQ <- lm(qsec ~ wt + cyl + hp + am, data=mtcars)
qsecP <- predict(modelQ, 
newdata = data.frame(wt = 1, cyl = 4, hp = 90, am = 0))
dataTableSelect[dataTableSelect$qsec >=  qsecP,]
```
## Conclusion
- This application revolutionizes the car design and buying process
- Uses histroical data to help shape future decisions
